---
title: "Homework 1"
author: "Ayeshra Acharya"
date: "9/15/2020"
output: github_document
---

```{r}
library(tidyverse)
```

## Problem 1

Create a data frame with the specified elements. 

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Take the mean of each variable in the data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```
I can take the mean of numbers and logical but not character or factor. 
```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```
```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```
## Problem 2
data("penguins", package = "palmerpenguins")
view(penguins)
## The penguins dataset consists of the variables species, island, bill length, bill depth, flipper length, body mass, sex, and year. The 3 species of penguins included this dataset are: adelie, gentoo, and chinstrap. The islands that these penguins are in as reflected in the dataset include: Torgersen, Biscoe, and Dream. There are some missing variables in the data. 

```{r}
nrow(penguins)
ncol(penguins)
```
## The dataset consists of 344 rows and 8 columns. 

Finding the mean flipper length. 
```{r}
summary(penguins$bill_length_mm)
```
##The mean flipper length is 43.92. 

Making a scatterplot. 

